% LaTeX resume using res.cls
\documentclass[line, margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt}
\usepackage{hyperref}
\usepackage{beramono}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0.5pt}
\setlength{\partopsep}{0.5pt}
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

\name{\Large Ford Higgins}

\begin{resume}
	
	
\section{Contact \\ Information}
	+1 925 336 7529       \hfill \href{https://linkedin.com/in/wfordh/}{linkedin.com/in/wfordh} \\
	\noindent higgins.ford@gmail.com  \hfill \href{https://github.com/wfordh}{github.com/wfordh} \\
	\noindent San Francisco, CA 94108
	% \noindent Charlotte, NC 28226
	

\section{Languages}
	Python (Pandas, NumPy, scikit-learn, Seaborn, command line scripts), SQL (PostgreSQL, Redshift, MySQL), R (Tidyverse, ggplot2), Git, zsh
	
\section{Tools}
	Periscope, Github, Airflow, Google Maps and Drive APIs, Kepler.gl, Jupyter Notebooks, AWS (EC2, S3), Excel, JIRA, Airtable


\section{Work\\Experience}
	\textbf{Scoop Technologies} \hfill{San Francisco, CA} \vspace{1 mm}\\\vspace{0.5mm}%
	\textsl{Data Analyst} \hfill{January 2019 -- November 2020}\
	\begin{itemize}
		\item Improved the monthly reporting process by decreasing time spent by 80\% with Python scripts, the Google Drive API, and Airflow.
		\item Helped the Sales team increase conversion rate with a custom geo-visualization Python script using the Google Maps API, transit data, and Uber's Kepler.gl.
		\item Collaborated with diverse stakeholders on projects such as creating Periscope dashboards, modeling user lifetime value for Finance, pulling targeting email lists for Marketing, and launching Diversity, Equity, and Inclusion initiatives.
		\item Worked with Product, Design, and Engineering on new features by defining KPIs, creating analytics events, and analyzing post-launch performance.
	\end{itemize}\
	
	\textbf{Bracket Voodoo/Lot 10 Sports} \hfill{San Francisco, CA} \vspace{1mm}\\\vspace{0.5mm}%
	\textsl{Data Science Intern} \hfill {October 2017 -- October 2018}\
	\begin{itemize}
		\item Created a new football metric measuring field control, with analysis from the 2017 NCAA season using Pandas, Plotly, and Seaborn.
		\item Improved the predictive accuracy of NCAA basketball statistical systems to 75\% using a hierarchical Bayesian regression model with Pandas and scikit-learn.
		% \item Ranked, verified, and assessed the accuracy of the basketball systems using Pandas, Matplotlib, and MySQL.
		\item Classified NCAA football teams as part of a project creating a 'football genome' using Pandas, Matplotlib, and PostgreSQL.
	\end{itemize}\

	\textbf{NBA} \hfill{Secaucus, NJ} \vspace{1mm}\\\vspace{0.5mm}%
	\textsl{Game Reviewer} \hfill {September 2016 -- June 2017}\
	\begin{itemize}
		\item Reviewed and evaluated referee performance in NBA games, including the NBA Playoffs, based on the quality and correctness of their calls and non-calls.
		%\item Periodically reviewed the last two minutes of close games as the first step of the Last 2 Minute review process. %, where attention to detail was imperative since the final product is public.
	\end{itemize}
	
	
\section{Education}
	\textbf{University of San Francisco}, San Francisco, CA \vspace{1mm}\\\vspace{1mm}
	\textsl{MS, Data Science} \hfill {July 2017 -- June 2018}\

	\textbf{Davidson College}, Davidson, NC \vspace{1mm}\\\vspace{-1mm}
	\textsl{BS, Mathematics} \hfill {August 2010 -- May 2014}


\section{Projects}
%	\textbf{PyBaseball:}  Developed functions for pulling data from StatCast leaderboards
	
%	\textbf{Her Hoop Stats:} Writing back end code for additional statistics and features for the website

%	\textbf{D3 Hoop Stats}
%	\begin{itemize}
%		\item Creating a website for Division 3 men's basketball statistics
%		\item Implementing full stack JS solution using Sportsdataverse, Postgres, and Gatsby 
%	\end{itemize}
	\textbf{Parking Availability in San Francisco} \hfill{March 2018}
	\begin{itemize}
		\item Predicted parking availability using public data from sensors and parking meters in addition to a proprietary dataset.
		\item Employed gradient boosting models (LightGBM, XGBoost, and CatBoost) and random forest classifiers to fit the data before optimizing the hyperparameters. %Tuned hyperparameters and performed feature engineering to optimize results.
	\end{itemize} \

%	\textbf{Prediction of Canadian Bankruptcy Rates} \hfill{December 2017}
%	\begin{itemize}
%		\item Forecasted Canadian bankruptcy rates using financial time-series data using SARIMAX, VAR, and Holt-Winters methods.
%	\end{itemize}
		
\section{Leadership}
	% \textbf{Davidson Men's Basketball}, Davidson, NC \vspace{1mm}\\\vspace{0.5mm}%
	% \textsl{Head Student Manager} \
	% \begin{itemize}
	%   \item  Four-year student manager; promoted to head manager prior to senior season.
	% \end{itemize}
	% \textbf{Boy Scouts} \vspace{1mm}\\\vspace{1mm}%
	% \textbf{Eagle Scout} \hfill {May 2010}
	Eagle Scout \hfill {May 2010}
	% \begin{itemize}
	%   \item Earned rank of Eagle in May of 2010 and Bronze Palm in August of 2010.
	% \end{itemize}


\end{resume}
\end{document}




